Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-20 cordillera-cycle.tex
Isolate multi-record timeseries plotting script.
Remove hi-res snapshots and timeseries.
For the moment I don't see the use of them.

All six simulations consistently produce two major glaciations during MIS~4 and
MIS~2 (Figs.~\ref{fig:multirec-timeseries} and~\ref{fig:multirec-snapshots}).
However the timing is much different. Notably the oceanic core forcing result
in much too early last glacial maximum.

@@

We re-run the GRIP (?) and Vostok (?) core simulations at higher resolution
(Figs.~\ref{fig:hires-timeseries} and ~\ref{fig:hires-snapshots}). Results are
consistent with lower resolution but differences appear due to small-scale
topography better capturing mass-balance lapse-rate effects. In general the
Greenland-based simulation show much more variability.

@@

% fig:multirec-timeseries
\begin{figure}
  \includegraphics{multirec-timeseries}
  \caption{Multi-record timeseries. In construction.
           \todo{Add NGRIP}
           \idea{Use same colors but different patterns for similar records}}
  \label{fig:multirec-timeseries}
\end{figure}

% fig:multirec-snapshots
\begin{figure}
  \includegraphics{multirec-snapshots}
  \caption{Multi-record snapshots. In construction.
           \todo{Add NGRIP}}
  \label{fig:multirec-snapshots}
\end{figure}

% fig:hires-timeseries
\begin{figure}
  \includegraphics{hires-timeseries}
  \caption{High resolution timeseries. In construction.
           \todo{Use same scaling at low and high resolution}
           \idea{Compare to low-resolution}}
  \label{fig:hires-timeseries}
\end{figure}

% fig:hires-snapshots
\begin{figure}
  \includegraphics{hires-snapshots}
  \caption{High resolution snapshots. In construction.
           \idea{Fewer snapshots, bigger figure}}
  \label{fig:hires-snapshots}
\end{figure}

>>>>

All six simulations consistently produce two major glaciations during MIS~4 and
MIS~2 (Figs.~\ref{fig:timeseries} and~\ref{fig:multirec}).
However the timing is much different. Notably the oceanic core forcing result
in much too early last glacial maximum.

@@

We re-run the GRIP (?) and Vostok (?) core simulations at higher resolution.
Results are
consistent with lower resolution but differences appear due to small-scale
topography better capturing mass-balance lapse-rate effects. In general the
Greenland-based simulation show much more variability.

@@

% fig:multirec-timeseries
\begin{figure}
  \includegraphics{timeseries}
  \caption{Multi-record timeseries. In construction.
           \todo{Add NGRIP}
           \idea{Use same colors but different patterns for similar records}}
  \label{fig:timeseries}
\end{figure}

% fig:multirec-snapshots
\begin{figure}
  \includegraphics{multirec}
  \caption{Multi-record snapshots. In construction.
           \todo{Add NGRIP}}
  \label{fig:multirec}
\end{figure}
